Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-03-31 bbbq_article.tex
Improve figures, progress #199
Figures have readable texts, fix #199

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.95\textwidth]{bbbq_1_smart_results/fig_f_tmh_2_panel}
  \caption{
    TMH-derived peptides are predicted to be over-presented in general,
    which is for MHC-I (left column) and MHC-II (right column),
    as well as for the proteomes of SARS-CoV-2 (top row), human (middle 
    row) and \emph{M. tuberculosis} (bottom row).
    The bars show the percentage of epitopes predicted to be 
    overlapping with TMHs.
    The red lines indicate the percentage as expected by chance.
    See supplementary tables \ref{tab:tmh_binders_mhc1} and \ref{tab:tmh_binders_mhc2}
    for the exact TMH and  epitope counts.
    \richel{Decide in meeting: add panel with hydrophobicity}
  }
  \label{fig:bbbq_1_smart_results}
\end{figure}

@@

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{ncbi_peregrine_results/fig_conservation_per_spanner.png}
    \label{fig:conservation_per_spanner}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{ncbi_peregrine_results/fig_f_tmh_ncbi.png}
    \label{fig:f_tmh_ncbi_per_spanner}
  \end{subfigure}

@@

  \begin{subfigure}[t]{\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{ncbi_peregrine_results/fig_f_snps_found_and_expected_per_spanner.png}
    \label{fig:f_snps_found_and_expected_per_spanner}
  \end{subfigure}
  \caption{
      \textbf{(A)} 
      The number of SNPs in TMHs as expected by chance (red bars) 
      and found in the dbSNP database (right bars), 
      after splitting the data into single- and multi-spanners.
      Percentages are added to show the relative conservation
      of SNPs in TMHs found.
      \textbf{(B)} 
      \richel{THIS IS A PLACEHOLDER}
      Distribution of the proportion of amino acids residing
      in the plasma membrane.
      \textbf{(C)} 
      Percentage of SNPs found in TMPs predicted to have only a single
      (left) or multiple (right) TMHs.
      The dashed diagonal lines show the expected line of equality 
      (i.e., equal conservation of TMHs and solvent-exposed 
      protein regions).
  }
\end{figure}

>>>>

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.95\textwidth]{bbbq_1_smart_results/fig_f_tmh_2_panel}
  \caption{
    TMH-derived peptides are predicted to be over-presented in general,
    which is for MHC-I (left column) and MHC-II (right column),
    as well as for the proteomes of SARS-CoV-2 (top row), human (middle 
    row) and \emph{M. tuberculosis} (bottom row).
    The bars show the percentage of epitopes predicted to be 
    overlapping with TMHs.
    The red lines indicate the percentage as expected by chance.
    See supplementary tables \ref{tab:tmh_binders_mhc1} and \ref{tab:tmh_binders_mhc2}
    for the exact TMH and  epitope counts.
    \richel{Add panel with hydrophobicity?}
  }
  \label{fig:bbbq_1_smart_results}
\end{figure}

@@

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{ncbi_peregrine_results/fig_conservation_per_spanner.png}
    \label{fig:conservation_per_spanner}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{ncbi_peregrine_results/fig_f_tmh_ncbi_per_spanner.png}
    \label{fig:f_tmh_ncbi_per_spanner}
  \end{subfigure}

@@

  \begin{subfigure}[t]{\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{ncbi_peregrine_results/fig_f_snps_found_and_expected_per_spanner.png}
    \label{fig:f_snps_found_and_expected_per_spanner}
  \end{subfigure}
  \caption{
      \textbf{(A)} 
      The number of SNPs in TMHs as expected by chance (red bars) 
      and found in the dbSNP database (right bars), 
      after splitting the data into single- and multi-spanners.
      Percentages are added to show the relative conservation
      of SNPs in TMHs found.
      \textbf{(B)} 
      Distribution of the proportion of amino acids residing
      in the plasma membrane.
      \textbf{(C)} 
      Percentage of SNPs found in TMPs predicted to have only a single
      (left) or multiple (right) TMHs.
      The dashed diagonal lines show the expected line of equality 
      (i.e., equal conservation of TMHs and solvent-exposed 
      protein regions).
  }
\end{figure}
